% Credit to the scimisc-cv.sty template from Scimisc (on Overleaf)
\documentclass{article}
\usepackage{scimisc-cv}

\title{Resume}
\author{Franz Anthony Varela (Template courtesy of Scimisc)}
\date{November 2025}

%% These are custom commands defined in scimisc-cv.sty
\cvname{Franz Anthony Varela}
\cvpersonalinfo{
Seattle, WA \cvinfosep
916-430-2109 \cvinfosep
franzanthonyvarela@gmail.com \cvinfosep
LinkedIn: Franz Anthony Varela
}

\begin{document}

\makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo


\section{Education}
\cvsubsection{University of Washington, Bothell}[Bothell, WA][M.S. in CS\&SE (\textbf{GPA:3.80})][Sep 2020 - Jun 2022]
\begin{itemize}
    \item \textbf{Relevant Coursework}: Internet of Things | Machine Learning | High Performance Computing | Advanced Computer Graphics | Advanced Topics in Computer Vision
\end{itemize}
\cvsubsection{University of California, Merced}[Merced, CA][B.S. in CS\&E (\textbf{GPA:3.82})][Aug 2017 - May 2020]
\begin{itemize}
  \item Graduated with High Honors 
  \item \textbf{Relevant Coursework}: Deep and Reinforcement Learning | Software Engineering | Numerical Methods | Database Systems | Computer Architecture | Linear Analysis | Algorithm Design and Analysis | Object-Oriented Programming
\end{itemize}

\section{Technical Skills}
\begin{itemize}
  \item Languages: Rust, C/C++, Kotlin, Java, Python, SQL, \LaTeX{}
  \item Frameworks/Tools: PyTorch, TensorFlow, SciKit‑Learn, OpenCV, CUDA, Unity, Blender, OpenGL, WebGPU (WGPU), Bevy
  \item Platforms: Linux, Windows, MacOS, Android, Arduino
  \item Other: Git, Jupyter Notebook, FL Studio, Aseprite
\end{itemize}

\section{Work Experience}
\cvsubsection{Amazon -- Leo (previously Kuiper)}[Redmond, WA][SDE II][Mar 2025 - Present]
\begin{itemize}
  \item Engineered Rust-based Fault Detection, Isolation, and Recovery (FDIR) system for production satellite infrastructure, ensuring performance and space safety
  \item Reduced RCA time from hours to minutes by automating log downlinking, streamlining operational workflows
  \item Modernized FDIR codebase with idiomatic Rust practices, improving maintainability and enabling faster feature development
\end{itemize}
\cvsubsection{Amazon -- Alexa Auto}[Santa Clara, CA][SDE I/II][Feb 2022 - Mar 2025]
\begin{itemize}
  \item Led overhaul of Alexa Auto App UI/UX, deployed across multiple OEM trims.
  \item Developed proof‑of‑concept feature integrating smart home cameras into automotive head units via voice commands.
  \item Championed adoption of modern Android practices (Kotlin, dependency injection with Hilt), improving code quality and scalability.
\end{itemize}
\cvsubsection{Amazon -- Alexa Auto}[Santa Clara, CA][SDE I Intern][Jun 2021 - Aug 2021]
\begin{itemize}
  \item Designed and integrated App Launch module in Auto SDK and AACS, written in C++11 and Java.
  \item Leveraged Alexa for Apps API to enable seamless automotive app integration.
\end{itemize}

\section{Research}
\cvsubsection{Master's Thesis "The Effects of Hybrid Neural Networks on Meta-Learning Objectives"}[Merced, CA][Author][Jun 2021 - Feb 2022]
\begin{itemize}
  \item Designed and implemented hybrid neural network architecture Knowledge Representation + Task Inference (KR+TI) to explore generalization in meta-learning on a small scale. 
  \item Investigated autoencoder variants (vanilla, variational, Hopfield-based) as reusable representation modules for meta-learning tasks.
  \item Published findings on catastrophic forgetting and dataset complexity effects, contributing to the broader discourse on Artificial General Intelligence (AGI).
  \item Validated model interpretability by visualizing autoencoder reconstructions and analyzing representation reuse across tasks.

\end{itemize}
\cvsubsection{"2-Dimensional Online Scheduling"}[Merced, CA][Undergraduate Researcher][Jul 2019 - Aug 2019]
\begin{itemize}
  \item Developed algorithms in C++ to analyze low‑dimensional online scheduling problems.
  \item Evaluated runtime performance and correctness of the Priority(Max) algorithm.
\end{itemize}

\section{Projects}
\cvsubsection{Project SoundFrame}[Seattle, WA][Solo Developer][Jan 2025 - Present]
\begin{itemize}
  \item Developing a faithful yet original remake of "Steambot Chronicles" in Rust, with the Bevy ECS framework
  \item Spearheading full‑stack development and creative production, including gameplay systems, original music composition (FL Studio), and 3D asset creation (Blender).

\end{itemize}

\end{document}
